---
title: "Simple document"
author: "Will Anderson"
date: 2022-09-13
output: github_document
  
---
 <!-- toc: true
    toc_float: true
    code_folding: hide -->
<!--
I'd like to save this text for later and don't want to delete it yet.
-->

<!-- echo suppresses the code in the formatted document, message suppresses all the library outputs, eval does not execute the code -->

<!-- to change to pdf you must type output: pdf_document -->

$y = mx + b$ <!-- good looking math equations use bookended dollar signs -->

# This is my own header
```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is going to make a plot! First I generate a dataframe, then use ggplot to make a scatterplot
Echo doesn't show the code in output 
```{r, chunk_scatterplot} 
plot_df=
  tibble(
    x=rnorm(n=1000),
    y=1+2*x+rnorm(n=1000)
  )

ggplot(plot_df,aes(x=x,y=y))+geom_point()

```

```{r, echo = FALSE}
my_tib = tibble(
  
my_var = rnorm(n = 500, mean = 1),

log_vec = my_var > 0,

numeric_vec = abs(my_var)
)

ggplot(my_tib,aes(x = numeric_vec)) + geom_histogram()

my_median = median(my_tib$my_var)

```
The median of the data is `r round(my_median,2)`

```{r}
mean1 = mean(my_tib$my_var)
median1 = median(my_tib$my_var)
stdev1 = sd(my_tib$my_var)

```
* The mean is `r mean1`
  * The median is `r median1`
  * The standard deviation is `r stdev1`

#Header1   